|

### 2023-03-01 paper_comparison/paper_comparison/paper_comparison.Rmd
tweak the points in power cmp plot

  # Group the data by effect and reject to draw points
  geom_point(data = visual_poly_dat %>%
               mutate(log_effect_size = log(effect_size)) %>%
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject, size = num_response), 
             alpha = 0.3) +

@@

  # Group the data by effect and reject to draw points
  geom_point(data = visual_heter_dat %>%
               mutate(log_effect_size = log(effect_size)) %>%
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject, size = num_response), 
             alpha = 0.3) +

>>>>

  geom_point(data = visual_poly_dat,
             aes(log(effect_size), reject),
             alpha = 0.15) +

@@

  geom_point(data = visual_heter_dat,
             aes(log(effect_size), reject),
             alpha = 0.15) +
